Legal basis for replacing handwritten signatures with open electronic signature software

### 2020-01-29 articles/legal basis.tex
Update legal basis article

Signing of documents is something we get used as we get older.
It is usually expected we will sign a real paper document.
How easy it is if we want to sign some documents without meeting with another party in person?
Do we print the documents from their electronic form only because we need to sign them? There is an alternative in the form of electronic signatures.
On what legal ground can we do so and what if we also want to make it a part of open-source movement?

Unless specified otherwise, we are considering law applicable locally in the Slovak Republic (SR).
Its law is greatly influenced by the European Union (EU), being its member since 2004, and to some extent by the rest of the world.
Therefore, we can assume this is at least partially applicable outside of the SR.

@@

Essential part of the written legally binding documents, they are permanently affixed to the document and are supposed to uniquely identify the person and its deliberate, informed consent.
As can be seen in the Slovak Civil Code, "A written legal act is valid if signed by the acting person;" \cite{1}.
Law often explicitly requires signatures and further clarifies their expected use.
For example, when selling an enterprise, the contract is required in written form and attested signatures of the seller and the buyer \cite{2}.

>>>>

We are usually used to signing of paper documents.
How easy it is if we want to sign some documents without meeting with another party in person?
Do we print the documents from their electronic form only because we need to sign them? There is an alternative in the form of electronic signatures.
We would like to explore on what legal ground we can do so and what if we also want to make it a part of the open-source movement.

Unless specified otherwise, we are considering law applicable locally in the Slovak Republic (SR).
Its law is greatly influenced by the European Union (EU), being its member since 2004, and therefore, we can assume this is at least partially applicable outside of the SR.

@@

Essential part of the written legally binding documents, signatures are permanently affixed to the document and are supposed to uniquely identify the person and its deliberate, informed consent.
As can be seen in the Slovak Civil Code, "A written legal act is valid if signed by the acting person;" \cite{1}.
Law often explicitly requires signatures and further clarifies their expected use.
For example, when selling an enterprise, the contract is required in written form, with attested signatures of the seller and the buyer \cite{2}.
